\chapter{Grundlagen/Fundamentals}
\section{Cryptography}

Cryptography is the science of securing information through encryption. Encryption or ciphering refers to the process of making a message incomprehensible \cite[18]{crypto} The security of all cryptographic methods is essentially based on the difficulty of guessing a secret key or obtaining it by other means. It is possible to guess a key, even if the probability becomes very small as the length of the key increases. It must be pointed out that there is no absolute security in cryptography \cite[25]{crypto}.

Practically all cryptographic methods have the task of ensuring one of the following security properties are met \cite[18]{crypto}. 
\begin{itemize}
    \item \textbf{Confidentiality} The aim of confidentiality is to make it impossible or difficult for unathorized persons to read a message \cite[18]{crypto}.
    \item \textbf{Authenticity} Proof of identity of the message sender to the recipient, i.e. the recipient can be sure that the message does not originate from another (unauthorized) sender \cite[18]{crypto}
    \item \textbf{Integrity} The message must not be altered (by unauthorized persons) during transmission. It retains its integrity \cite[18]{crypto}.
    \item \textbf{Non-repudiation} The sender cannot later deny having sent a message \cite[18]{crypto}.
\end{itemize}

Cryptographic algorithms are mathematical equations, i.e. mathematical functions for encryption and decryption \cite[19]{crypto}. A cryptographic algorithm for encryption can be used in a variety of ways in different applications. To ensure that an application always runs in the same and correct correct way, cryptographic protocols are defined. In contrast to the cryptographic algorithms, the protocols are procedures for controlling the flow of transactions for certain applications. \cite[22]{crypto}.

The idea of combining cryptographic methods with voting systems is not new. In 1981, David Chaum published a cryptographic technique based on public key cryptography that hides who a participant communicates with, aswell as the content of the communication. The untracable mail system requires messages to pass through a cascade of mixes (also known as a Mix Network) \cite[86]{chaum}. Chaum proposes that the techniques can be used in elections in which an individual can correspond with a record-keeping organisation or an interested party under a unique pseudonym. The unique pseudonym has to appear in a roster of accetable clients. A interested party or record keeping organisation can verify that the message was sent by a registered voter. The record-keeping organisation or the interested party can also verify that the message was not altered during transmission. \cite[84]{chaum}. 

In this use case, the properties of Confidentiality, Authenticity, Integrity and Non-repudiation are ensured. However, to be worthy of public trust, an election process must give voters and observers compelling evidence that the election was conducted properly without breaking voters confidentiality. The problem of public trust is further exacerbated to now having to trust election software and hardware, in addition to election officials, and proceedurs.

In 2021, the U.S. Election Assitance Commission (EAC) adopted the Voluntary Voting System Guidelines (VVSG) 2.0. \cite{https://www.eac.gov news/2021/02/10 us-election-assistance-commission-adopts-new-voluntary-voting-system-guidelines-20}. The VVSG is intended for designers and manufacturers of voting systems. Currently, the VVSG is titled as "Recommendations to the EAC" because it's not yet the final version that voting system manufacturers will follow.
\cite{https://www.nist.gov/itl/voting/vvsg-introduction}. The VVSG 2.0 currently states only two methods for achieving software independence. The first through the use of independent voter-verifiable paper records, and the second through cryptographic E2E verifiable voting systems. The VVSG 2.0 states that a voting system need to be software independent through the use of independent voter-verifiable paper records
\cite[181]{https://www.eac.gov/sites/default/files/TestingCertification/Voluntary_Voting_System_Guidelines_Version_2_0.pdf}. However, due to the lack of E2E verifiable voting systems available within the current market, there are no verified E2E cryptographic protocols.\cite[199]{https://www.eac.gov/sites/default/files/TestingCertification/Voluntary_Voting_System_Guidelines_Version_2_0.pdf} The U.S. Election Assistance Commission, in collaboration with the National Institute of Standards and Technology initialised an Call for proposals to solicit, evaluate, and approve protocols used in E2E cryptographically verifiable voting systems. \cite{https://www.eac.gov/voting-equipment/end-end-e2e-protocol-evaluation-process}. 

Submitted protocols must support the following properties
\begin{itemize}
      \item Cast as Intended: Allow voters to confirm the voting system correctly interpreted their ballot selections while in the polling place via a receipt and provide evidence such that if there is an error or flaw in the interpretation of the voters’ selections.
      \item Recorded as Cast: Allow voters to verify that their cast ballots were accurately recorded by the voting system and included in the public records of encoded ballots.
      \item Tallied as Recorded: Provide a publicly verifiable tabulation process from the public records of encoded ballots.
\end{itemize}

\section{ElectionGuard}

One of the first pilots to see how E2E verifiable elections works in a real election took place in a district of Preston, Idaho, United States, on November 8, 2022. The Verity scanner from Hart InterCivic was used in this pilot, which was integrated with Microsoft's ElectionGuard. [EAC Report]. ElectionGuard is a toolkit that encapsulates cryptographic functionality and provides simple interfaces that can be used without cryptographic expertise. The principal innovation of ElectionGuard is the seperation of the cryptographic tools from the core mechanics and user interfaces of voting systems. In it's preferred deployment, ElectionGuard doesn't replace the existing vote counting infrastructure but instead runs alongside and produces its own independently-verifiable tallies \cite[1-2]{eg-paper}. The cryptographic design is largely inspired by the cryptographic voting protocol by Cohen (now Benaloh) and Fischer in 1985 and the voting protocol by Cramer, Gennaro and Schoenmakers in 1997 \cite[5]{eg-paper}. 

----------------------------------------------
The philosophy of ElectionGuard has been to cover the majority of voting scenarios with an approach that is as simple as possible to understand and verify. It can be used with Precinct Ballot Scanners, Electronic Ballot Markers, Internet Voting, Risk-Limiting Audits and even vote by mail and many more.

In all applications, an election using ElectionGuard begins with a key-generation ceremony in
which an election administrator works with guardians to form election keys. Later, usually at the
conclusion, the administrator will again work with guardians to produce verifiable tallies. What
happens in between, however, can vary widely. [ElectionGuard: a Cryptographic Toolkit
to Enable Verifiable Elections].

This thesis focuses on the implementation of the Key Generation Ceremony and the Guardians using the ESP32 microcontroller. The ESP32 is a low-cost, low-power system on a chip microcontroller. It is widely used in IoT applications. [source]
----------------------------------------------
\subsection{Election Verification}
ElectionGuard support the central aspects which a VVSG 2.0 compliant voting system must support Cast as Intended, Recorded as Cast and Tallied as Recorded. \cite[17]{eg-paper}. Key element supporting cast-as-intended and recorded-as-cast verifiability is through confirmation codes. Ballots can be ce challenged or cast and both are included in the election record. Voters can check if the expected confirmation code appears in the election records and for the challenged ballots, that it shows the correct selections \cite[18]{eg-paper}. Tallied-as-cast verifiability is supported through the inclusion of all ballots and decryption proofs in the election record. Any voter can verify that the ballot is accurately incorporated in the tally, and the decryption proofs demonstrate the validity of the announced tally \cite[18]{eg-paper}. To confirm the election's integrity, independent verification software can be used at any time after the completion of an election. \cite[6]{eg-paper}. Some, may choose even to write their own verifiers.  



One such E2E verifiable voting protocol is ElectionGuard which will be implemented in this thesis. Before proceeding several cryptographic techniques need to be introduced first.

End-to-end verifiable election techniques enable individual voters to check crucial ingredients
of election results – without requiring voters to trust election software, hardware, election
officials, procedures, or even observers. Voters may check these ingredients themselves, place their
trust in others of their choice (e.g. their preferred candidates, news media, and/or interest groups),
or accept the outcome produced with the usual administrative safeguards
page1

Any chain of evidence, for any system design, requires some assumptions. Checking that those
assumptions hold for the election in question is crucial. Trusting unverifiable hardware or software is
generally not reasonable. Trusting processes for secure handling of paper ballots may, or may not,
be reasonable, depending on what those processes are and how they can be observed. E2E-V
systems are software independent and do not rely on trusted paper processes, instead providing
opportunities to verify the election outcome electronically
page2

End-to-end verifiable voting schemes provide ways of performing these tasks.


ElectionGuard's approach to End-to-End Verifiable Elections

Core Principles of ElectionGuard
Guardian key and tally ceremonies
Generation of ballot confirmation code
Cofnirmation-code lookup Seite
Ability to challenge ballots
Verifier support

Integrating ElectionGuard's key ceremony with ESP32


\section{ElectionGuard}


ElectionGuard is not a complete election system. It instead provides components for system developers to implement
E2E-verifiable elections. The goal of ElectionGuard is to promote voter confidence by empowering voters to
indepently verify the accuracy of election results. \cite[1]{eg-spec}



ElectionGuard achieves this by

\subsection{Verifier Construction}
the signature. The entire election record and its digital signature should be
\cite[25]{eg-spec}
published and made available for full download by any interested individuals. Tools should also be provided for easy
look up of tracking codes by voters.
\cite[25]{eg-spec}

\subsection{ElectionGuard Components}
Four Principal components of ElectionGuard are described below \cite[3-4]{eg-spec}
\begin{itemize}
    \item[Parameter Requirements] These are properties required of parameters that are standard in every election. A
          specific set of standard parameters is provided [...].
    \item[Key Generation] Prior to each individual election, guardians must generate individual publicprivate key
          pairs and exchange shares of private keys to enable completion of an election even if some guardians become
          unavailable.
    \item[Ballot Encryption] While encrypting the contents of a ballot is a relatively simple operation, most of the
          work of ElectionGuard is the process of creating externally-verifiable artifacts to prove that each
          encrypted ballot is well-formed (i.e., its decryption is a legitimate ballot without overvotes or improper values).
    \item[Verifiable Decryption]
          At the conclusion of each election, guardians use their private keys to produce election tallies
          together with verifiable artifacts that prove that the tallies are correct.
\end{itemize}

\subsubsection{Parameter Requirements}


\subsubsection{Ballot Encryption}
Ballot encryption In most uses, the election system makes a single call to the ElectionGuard API after each voter
completes the process of making selections [...]. ElectionGuard will encrypt
the selections made by the voter and return a verification code which the system should give to the voter.1
\cite[3]{eg-spec}

The encrypted ballots are published along with non-interactive zero-knowledge proofs of their integrity. The encryption
method used herein has a homomorphic property which allows the encrypted ballots to be combined into a single aggregate
ballot which consists of encryptions of the election tallies.
\cite[3]{eg-spec}

Encryption of votes in ElectionGuard is performed using an exponential form of the ElGamal cryptosystem4.
\cite[4]{eg-spec}.

An encryption of one is used to indicate that an option is selected, and an encryption of zero is used to indicate that
an option is not selected.\cite[5]{eg-spec}

Homomorphic properties A fundamental quality of the exponential form of ElGamal described above is its additively
homomorphic property. If two messages M1 and M2 are respectively encrypted as $(A1, B1) = (gR1 mod p, gM1 \cdot KR1 mod p)
    and (A2, B2) = (gR2 mod p, gM2 \cdot KR2 mod p)$ ,then the componentwise product $(A, B) = (A1A2 mod p, B1B2 mod p) = (gR1+R2
    mod p, gM1+M2 \cdot KR1+R2 mod p)$ is an encryption of the sum $M1 + M2$.
\cite[5]{eg-spec}.

This additively homomorphic property is used in two important ways in ElectionGuard. First, all of the encryptions of a
single option across ballots can be multiplied to form an encryption of the sum of the individual values. Since the
individual values are one on ballots that select that option and zero otherwise, the sum is the tally of votes for that
option and the product of the individual encryptions is an encryption of the tally. The other use is to sum all of the
selections made in a single contest on a single ballot. After demonstrating that each option is an encryption of either
zero or one, the product of the encryptions indicates the number of options that are encryptions of one, and this can be
used to show that no more ones than permitted are among the encrypted options – i.e., that no more options were selected
than permitted. However, as will be described below, it is possible for a holder of a nonce R to prove to a third party
that a pair $(\alpha, \beta)$ is an encryption of M without revealing the nonce R and without access to the secret s.
\cite[5]{eg-spec}

Encryption of other data ElectionGuard provides means to encrypt data other than votes, which are selections encoded as
zero or one that need to be homomorphically aggregated. Such data may include the cryptographic shares of a guardian’s
private key that are sent to the other guardians and are encrypted to the receiving guardians’ public keys, write-in
information that needs to be attached to an encrypted selection and is encrypted to the election public key, or other
auxiliary data attached to an encrypted ballot, either encrypted to the election public key or to an administrative
public key. The non-vote data do not need to be homomorphically encrypted and can use a more standard form of public-key
encryption removing the data size restrictions imposed by the exponential ElGamal scheme for vote encryption.
ElectionGuard encrypts such data with hashed ElGamal encryption, which deploys a key derivation function (KDF) to
generate a key stream that is then XORed with the data. To implement the KDF and to provide a message authentication
code (MAC), encryption makes use of the keyed Hash Message Authentication Code HMAC. In ElectionGuard, HMAC is
instantiated as HMAC-SHA-256 with the hash function SHA-256.
\cite[7]{eg-spec}

\subsubsection{Verifiable Decryption}
After the conclusion of voting or
auditing, a quorum of guardians is necessary to produce the artifacts required to enable public verification of the
tally. \cite[2]{eg-spec}

Verifiable decryption
In the final step, election guardians independently use their secret keys to decrypt the election tallies and associated
verification data. It is not necessary for all guardians to be available to complete this step. If some guardians are
missing, a quorum of guardians can use the previously shared key fragments to reconstruct the missing verification data.
\cite[3]{eg-spec}

Observers can use this open specification and/or accompanying materials to write election verifiers that can confirm the
integrity of each encrypted ballot, the correct aggregation of these ballots, and the accurate decryption of election
tallies.
\cite[3]{eg-spec}


Threshold encryption Threshold ElGamal encryption is used for encryption of ballots and other data. This form of
encryption makes it very easy to combine individual guardian public keys into a single public key. It also offers a
homomorphic property that allows individual encrypted votes to be combined to form encrypted tallies. The guardians of
an election will each generate a public-private key pair. The public keys will then be combined (as described in the
following section) into a single election public key which is used to encrypt all selections made by voters in the
election. Ideally, at the conclusion of the election, each guardian will use its private key to form a verifiable
partial decryption of each tally. These partial decryptions will then be combined to form full verifiable decryptions of
the election tallies. To accommodate the possibility that one or more of the guardians will not be available at the
conclusion of the election to form their partial decryptions, the guardians will
\cite[6]{eg-spec}

\subsection{Parameter Requirements}
share11 their private keys amongst each other during key generation in a manner to be detailed in the next section. A
pre-determined threshold quorum value (k) out of the (n) guardians will be necessary to produce a full decryption.
\cite[7]{eg-spec}



Parameter Requirements Specific values for primes p and q and a generator g are given in Section 4 Baseline Parameters
below.
\cite[7]{eg-spec}




Note that decryption of individual ballots does not directly compromise voter privacy since links between encrypted
ballots and the voters who cast them are not retained by the system. However, voters receive verification codes that can
be associated with individual encrypted ballots, so any group that has the ability to decrypt individual ballots can
also coerce voters by demanding to see their tracking codes. Threshold ElGamal encryption is used for encryption of
ballots. This form of encryption makes it very easy to combine individual guardian public keys into a single public key
for encrypting votes and ballots. It also offers a homomorphic property that allows individual encrypted votes to be
combined to form encrypted tallies. The guardians of an election will each generate a public-private key pair. The
public keys will then be combined (as described in the following section) into a single election public key which is
used to encrypt all selections made by voters in the election. Ideally, at the conclusion of the election, each guardian
will use its private key to form a verifiable partial decryption of each tally. These partial decryptions will then be
combined to form full verifiable decryptions of the election tallies. To accommodate the possibility that one or more of
the guardians will not be available at the conclusion of the election to form their partial decryptions, the guardians
will cryptographically share13 their private keys amongst each other during key generation in a manner to be detailed in
the next section. A pre-determined threshold value (k) out of the (n) guardians will be necessary to produce a full
decryption.
\cite[8]{eg-spec}

\subsection{Ballot Encryption}
An ElectionGuard ballot is comprised entirely of encryptions of one (indicating selection made) and zero (indicating
selection not made). To enable homomorphic addition (for tallying), these values are exponentiated during encryption.
\cite[12]{eg-spec}

A contest in an election consists of a set of options together with a selection limit that indicates the number of
selections that are allowed to be made in that contest. In most elections, most contests have a selection limit
\cite[12]{eg-spec}

A legitimate vote in a contest consists of a set of selections with cardinality not exceeding the selection limit of
that contest. To accommodate legitimate undervotes, the internal representation of a contest is augmented with
“placeholder” options equal in number to the selection limit. Placeholder options are selected as necessary to force the
total number of selections made in a contest to be equal to the selection limit. When the selection limit is one, for
example, the single placeholder option can be thought of as a “none of the above” option. With larger selection limits,
the number of placeholder options selected corresponds to the number of additional options that a voter could have
selected
\cite[12]{eg-spec}
options selected corresponds to the number of additional options that a voter could have selected in a contest. For
efficiency, the placeholder options could be eliminated in an approval vote. However, to
\cite[12]{eg-spec}

Two things must now be proven about the encryption of each vote to ensure ballot integrity. 1. The encryption associated
with each option is either an encryption of zero or an encryption of one. 2. The sum of all encrypted values in each
contest is equal to the selection limit for that contest (usually one).
\cite[12]{eg-spec}

\subsection{Outline for proofs of ballot correctness}

The use of ElGamal encryption enables efficient zero-knowledge proofs of these requirements, and the Fiat-Shamir
heuristic can be used to make these proofs non-interactive. Chaum-Pedersen proofs are used to demonstrate that an
encryption is that of a specified value, and these are combined with the Cramer-Damg ard-Schoenmakers technique to show
that an encryption is that of one of a specified set of values – particularly that a value is an encryption of either
zero or one. The encryptions of selections in a contest are homomorphically combined, and the result is shown to be an
encryption of that contest’s selection limit – again using a Chaum-Pedersen
\cite[13]{eg-spec}
the result is shown to be an encryption of that contest’s selection limit – again using a Chaum-Pedersen proof.
\cite[13]{eg-spec}
The “random” nonces used for the ElGamal encryption of the ballot nonces are derived from a single 256-bit master nonce
RB for each ballot.
\cite[13]{eg-spec}

\subsection{Tracking codes}
Upon completion of the encryption of each ballot Bi, a tracking code Hi is prepared for each voter. The code is a
SHA-256 hash
\cite[17]{eg-spec}
previous tracking code. When the previous tracking code Hi is included, the chain is
The benefit of a chain is that it makes it more difficult for a malicious insider to selectively delete ballots and
tracking codes after an election without detection.
\cite[17]{eg-spec}

Once in possession of a tracking code (and never before), a voter is afforded an option to either cast the associated
ballot or spoil it and restart the ballot preparation process. The precise mechanism for voters to make these selections
may vary depending upon the instantiation, but this choice would ordinarily be made immediately after a voter is
presented with the tracking code, and the status of the ballot would be undetermined until the decision is made. It is
possible, for instance, for a voter to make the decision directly on the voting device, or a voter may instead be
afforded an option to deposit the ballot in a receptacle
\cite[17]{eg-spec}

\subsection{Ballot Aggregation}
At the conclusion of voting, all of the ballot encryptions are published in the election record together with the proofs
that the ballots are well-formed. Additionally, all of the encryptions of each option are homomorphically combined to
form an encryption of the total number of times that option was selected. The encryptions $(\alpha i, \beta i)$ of each individual
option are combined by forming the product $(A, B) = ( i \alpha i mod p,  i \beta i mod p)$. This aggregate encryption (A, B),
which represents an encryption of the tally of that option, is published in the election record for each option.
\cite[18]{eg-spec}



\subsection{Decryption of spoiled ballots}
Every ballot spoiled in an election is individually verifiably decrypted in exactly the same way that the aggregate
ballot of tallies is decrypted.
\cite[21]{eg-spec}

The exponential ElGamal used to encrypt votes is defined by a 4096-bit prime p and a 256-bit prime q which divides (p -
1). We use r = (p - 1)/q to denote the cofactor of q, and a
\cite[21]{eg-spec}

\subsection{The Election Record}
The record of an election should be a full accounting of all of the election artifacts. Specifically, it should contain
the following. Date and location of an election. The ballot coding file. The baseline parameters:
\cite[24]{eg-spec}



Every encrypted ballot prepared in the election (whether cast or spoiled): – All of the encrypted options on each ballot
(including “placeholder” options), – the proofs that each such value is an encryption of either zero or one, – the
selection limit for each contest, – the proof that the number of selections made matches the selection limit, – the
device information for the device that encrypted the ballot, – the date and time of the ballot encryption, – the tracker
code produced for the ballot. The decryption of each spoiled ballot: – The selections made on the ballot, – the
cleartext representation of the selections, – partial decryptions by each guardian of each option, – proofs of each
partial decryption, – shares of each missing partial decryption (if any), – proofs of shares of each missing partial
decryption (if any), – Lagrange coefficients used for replacement of any missing partial decryptions (if any). Tallies
\cite[24]{eg-spec}


Lagrange coefficients used for replacement of any missing partial decryptions (if any). Tallies of each option in an
election: – The encrypted tally of each option, – full decryptions of each encrypted tally, – cleartext representations
of each tally, – partial decryptions by each guardian of each tally, – proofs of partial decryption of each tally, –
shares of each missing partial decryption (if any), – proofs of shares of each missing partial decryption (if any), –
Lagrange coefficients used for replacement of any missing partial decryptions (if any). Ordered lists of the ballots
encrypted by each device. An election record should be digitally signed by election administrators together with the
date of 24
\cite[24]{eg-spec}
